---
title: "Final Exam"
author: "Catrina Terry"
date: 12/12/20
output: pdf_document
---





### What does it mean to do reproducible research? Why is reproducibility important to the process of science? (5 pts)


Reproducible research is when you can get the same results no matter the user analyzing the data. Any user can take the data, computational steps, methods, code and analysis and get the result and be able to replicate these results. Reproducibility is important to science because scientist across gradients can gain insight on a question without needing the manpower or funds to each reproduce this question. With this power we can gain more isngight and statistical prowess.













###  Using the data on red wine quality, develop a predictive model of red wine quality. Format the model in a way that it works well with the `predict` function in `R`. You will be assessed on the model structure mostly, but 5 of the 10 points will be on if the model can outperform a naive baseline (10 pts)



```{r}

dat <- read.csv('redWineTrain.csv')

###models
qtot<-lm(quality ~ fixed.acidity+  citric.acid+ residual.sugar+chlorides+free.sulfur.dioxide+total.sulfur.dioxide + pH +sulphates+alcohol,dat)
##exclude non significant variables from models
q1<-lm(quality ~ fixed.acidity+  citric.acid+ chlorides+free.sulfur.dioxide+total.sulfur.dioxide + pH +sulphates+alcohol,dat)
q2<-lm(quality ~   citric.acid+ chlorides+free.sulfur.dioxide+total.sulfur.dioxide + pH +sulphates+alcohol,dat) ###all significant
q3<-lm(quality ~  alcohol,dat) ###top  variables for simplicity sake

plot(qtot)
plot(q1)
plot(q2)
plot(q3)

#make range of value
x1=range(dat$alcohol) ###8.4-14
#x2=range(dat$sulphates) ###.33-1.95
#make range a seq
xalc <- seq(8,14, by=1)
#sul <-seq(.3,2, by=0.1)

yalc <- predict(q3, list(alcohol=xalc), type="response") ###predict response of alcohol to quality of wine
###make predictive plot
plot(dat$alcohol, dat$quality,pch=16, xlab="% alcohol", ylab = "Quality of Wine")
lines(xalc,yalc) ###plot line of predicted values
```



















### Pull data from an API of your choice (not Open Library), manipulate it in any way you choose, and create the most interesting and clear figure you can. (15 pts)

(See https://rapidapi.com/blog/most-popular-api/ for a list of APIs)

```{r}
library(httr)
library(jsonlite)
library(tidyverse)
#flight<- httr::GET('https://rapidapi.com/skyscanner/api/search.json?q=skyscanner')
             
 
 
flight <-httr::GET('https://rapidapi.com/blog/most-popular-api/search.json?q=skyscanner')
str(flight)
flightinfo <- jsonlite::fromJSON(content(flight,"text"),simplifyVector=FALSE)
flightconnection<- length(sum(sapply(flightinfo[[2]], function(x) { x$connections }))) 
plot(flightconnection)






```












### Use the R package `rgbif` to obtain occurrence data for a species of your choosing. Calculate the spatial distance between all occurrence points in a pair-wise fashion. (10 pts)



```{r}
###run into fatal error trying to install this  ¯\_(ツ)_/¯
library(rgbif)
wodu <- httr::GET('https://www.gbif.org/developer/species/Aix+ sponsa') #get wodu data
str(wodu)
woodduck <- rgbif::occ_search(scientificName = "Aix sponsa",
limit = 500, return='data')[[3]] ###obtain occupancy data of wood ducks
#calculate distance between points
library(geosphere)

wodu_distance<-distm(c(lon1, lat1), c(lon2, lat2), fun = distHaversine) # calculate distance between two points
##make for loop for all distances
emptyvec <- c()

f1 <- function(x) {
  for(i in 1:nrow(wodu_distance))
}
  
))
```



















### Write an R function that removes each value of a vector, calculates the mean of the modified vector, and then reports the overall mean and standard deviation of those vector means. (5 pts)


```{r}
getvect <- function(x) {
  x1<- 1:50 #create vector
  x2 <- x1[!x1%in% 30:50] ###remove some values
  return(mean(x2))
  return(mean(x1))
  return(sd(x1))
           }


```





















### Choose a software license that is one you would feel comfortable using and defend it's use over other licenses (5 pts)



I would choose MIT license because right now it is the one I am most comfortable with because it's easy to use, I can share content but I can also be private about it. I can share with collaborators if needed but keep things closed if collaborators want to work on it privately. It seems a lot more simple than other licenses and its one of the more common so most people would be comfortable using it. Plus no liability on the orignal author

















### Which of the following softwares are you likely to use in the future? (0 pts)

+ R
+ git
+ R markdown
+ the tidyverse
+ a Linux OS
+ bash shell







### What did you enjoy most about the course?


Learning the tidyverse package and other useful programming knowledge









### What could be improved for future iterations (especially as it will be geared more exclusively towards undergraduates in the future)?


There is no way "most" undergrads would be able to complete this course if it continues in this style. Too much of the work required for this class is not taught and the work is then not explained so there's no way to even know if you're doing things correctly. But this could be a great class if expectations were lower.








